---
title: "Homework 5"
author: "Jialiang Hua"
date: "11/16/2021"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
library(purrr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

read in the data

```{r message = FALSE}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ","),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>% 
  relocate(city_state) %>%
  filter(city_state != "Tulsa,AL")
```

The raw data consists of a case id, reported date of the case, the last name and the first name of the victim, the race, age and gender of the victim, the city and latitude, longitude the homicide was committed and the disposition.

Let's focus on Baltimore!

```{r}
homicount_df =
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolution == "unsolved")
  )
```

Let's do a prop.test for Baltimore

```{r}
prop.test(
  homicount_df %>% filter(city_state == "Baltimore,MD") %>% pull(hom_unsolved),
  homicount_df %>% filter(city_state == "Baltimore,MD") %>% pull(hom_total)) %>%
  broom::tidy()
```

iterate across the cities...

```{r}
result_df = 
  homicount_df %>% 
   mutate(
     prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n =.y)),
     tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
   ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

make a plot!

```{r}
result_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

Import the dataset
```{r  message = FALSE}
path_df =
  tibble(
    path = list.files("./data/data2")
  ) %>% 
  mutate(
    path = str_c("./data/data2/", path),
    observations = map(.x = path, ~read_csv(.x))
  ) %>% 
  separate(path, c("subject_id", "format"), sep = ".csv" ) %>% 
  separate(subject_id, c("format","subject_id"), sep = "2/" ) %>% 
  select(-format) %>% 
  separate(subject_id, c("arm","subject_id"), sep = "_") %>% 
  mutate(
    arm = case_when(
      arm == "con" ~ "control",
      arm == "exp" ~ "experiment")
  ) %>% 
  unnest(observations) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observations"
  ) %>% 
  mutate(
    week = str_replace(week,"week_",""),
    week = as.factor(week)) 
```

Make a spaghetti plot
```{r}
spaghetti_plot = 
  path_df %>%
  ggplot(aes(x = week, y = observations, group = arm, color = arm)) + 
  geom_path() +
  labs(
    title = "Observations of control group and experimental group",
    x = "Week",
    y = "Observation"
  )
ggsave("spaghetti_plot.jpg")
spaghetti_plot
```

Comment: In these eight weeks, we can finds that in experimental groups, the overall  observational values are higher than the control groups. And the trend of the experimental groups is increasing. As for the control groups, the trend is approximately fluctuating without apparent trend.


## Problem 3

introduces some missing values in each column. 

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

write a function...
```{r}
fill_in = function(vector) {
  
  if (is.numeric(vector)) {
    vector = replace(vector, is.na(vector), mean(vector, na.rm = TRUE))
  }
  
  else if (is.character(vector)) {
    vector = replace(vector, is.na(vector), "virginica")
  }
  
  else {
    stop("Data should be either number or character")
  }
  
  return(vector)
  
}
```

Apply the function
```{r}
iris_with_missing %>% 
  map_df(~ fill_in(.))
```

